Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-02 code/analysis.Rmd
2/3 of new analyses for lab meeting

cbind(pumpfinal, resid = residuals(fits)) %>%
  ggplot(aes(x = t, y = resid)) +
  geom_point() +
  geom_smooth()

@@

fitdata %>%
  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[t])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

final %>%
  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[s])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()
```

@@

>>>>

cbind(pumpfinal, resid = residuals(fits)) %>%
  ggplot(aes(x = t, y = resid, group = t)) +
  geom_violin(alpha = .05) +
  geom_smooth(inherit.aes = F, aes(x = t, y = resid))

@@

fitdata %>%
  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[t])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

final %>%
  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[s])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()
```

@@

## Addressing Laurel's comments on the outline

Most of Laurel's comments addressed the structure and written content of the paper. However, several recommended new analyses to include.

### 1: Finding $C$ for each level of $ad$, comparing to Fauria

**COMMENT:**

To better flesh out the role of stem density, you could consider figuring out what $C$ would be for each stem density, using the same functional form of the equation as Fauria. $C$ from our study and Fauria's study could be plotted against dimensionless stem density (i.e., $ad$ or solid volume fraction) to determine the nature of the relationship.

**ADDRESSED:**

Fauria's functional form was $CRe_c^{-1.14}R^{0.65}$. Excluding runs with biofilm, they got $C$ values of 1.53 and 3.18 for stem densities of 7209 (high) and 2724 (low) per meter, respectively.

Let's dig into stem density, frontal area, ad, etc.

Fauria didn't use cylinders but they give dimensions for their synthetic grass: average x-y plane cross-section was 3mm x 1mm, and it seems that they set water height to match stem height roughly. Given that their stems faced randomy in all directions, average *frontal* diameter per stem assuming a 3mm x 1mm rectangular prism (to avoid a multiple integral) would be approximated by, in mm,

$$\frac{\int_0^{\pi/2}[3\sin(\theta)+\cos(\theta)]\, \text{d}\theta}{\pi/2} = \frac{(1)-(-3)}{\pi/2}=\frac{8}{\pi}\,.$$

This, converted to meters, times stems per unit bed area gives frontal area per unit volume:  6.93 m$^{-1}$ (low) and 18.36 m$^{-1}$ (high).

$ad$ is frontal area per unit volume times diameter, making it dimensionless. Since it's unclear which $d_c$ to use for non-cylindrical objects, I'll just use that same frontal $d_c$ again: $8/\pi$. This yields $ad$ values of 0.0177 and 0.0467.

Solid volume fraction ($\phi$) is actually quite easy for rectangular prisms, and would theoretically be equivalent for the stems' actual, more trapezoidal shapes, if Fauria averaged correctly. It's simply $l \times w \times I_c$. This yields $\phi$ values of 0.00817 and 0.02163.

As for our values, cylinders make everything quite easy. We already have stem density and $ad$ in the table, and can calculate frontal area and $\phi$ with ease:

final <- final %>%
  mutate(frontal = ad/.003175, phi = ad*pi/4)

final %>%
  select(dowel_density, frontal, ad, phi) %>%
  distinct() %>%
  arrange(ad) %>%
  filter(ad>0)

Next, particle ratios: Fauria ran models across a range, but without LISST data, we only know $\eta$ for our particles altogether. Given our constant $d_c$ of 0.3175 cm and our median particle size of 25.2 microns, we'd get a particle-to-stem ratio of 
`r 25.2e-6/.3175e-2`. This raised to the .65 power gives a corrective term of 0.04312975.

OK, so now for the C value models:

cmods <- final %>%
  mutate(coeff = 0.04312975*Re^-1.14) %>%
  lmList(eta ~ 0 + coeff|phi, data = .)

So then, to put our results and Fauria's side by side:

c_over_phi <- cbind(rownames(coef(cmods))[2:4],coef(cmods)[2:4,]) %>%
  as.tibble() %>%
  mutate_all(as.numeric) %>%
  mutate(lab = "ESDL") %>%
  rename(phi = V1, C = V2)

fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria")

c_over_phi <- rbind(c_over_phi, fauria)

c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = lab)) +
  geom_point() +
  theme_bw()

### 2: Comparing Fauria model predictions to our observations

**COMMENT:**

If you use the same exponents as Fauria but treat C as a free parameter for each stem density configuration, how do predictions compare to the observations? This would be a plot either of Re vs eta for experimental data (points with error bars) and model predictions (lines) or of predicted vs. observed eta (with error bars for observed).

**ADDRESSED:**

# curve data 
fauria_pred <- tibble(Re = rep(seq(66,200,length = 1000),3), 
       C = c(rep(46.46556,1000),rep(10.987587,1000),rep(8.983344,1000)),
       phi = c(rep(0.002257447,1000),rep(0.006496250,1000),rep(0.011774453,1000))) %>%
  mutate(eta_est = Re^-1.14*C*0.04312975, ad = phi)

final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(phi,5)))) +
  geom_point() +
  geom_errorbar() +  
  geom_line(data = fauria_pred, aes(y = eta_est, x = Re), inherit.aes = FALSE) +
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~ as.character(round(phi,5))) +
  labs(y = "Effective capture efficiency", x = expression(Re), color = expression(phi)) +
  theme_bw()
